A thesis draft

### 2018-10-09 draft.tex
Merge Marco's TCP split part with mine

TUN/TAP and IP over IP maintain the connection transparency incapsulating the 
packet in another one. In this way, the original packet remains preserved and it 
becomes the new packet payload\todo{Make an image showing a packet inside 
another packet, to make easy to understand what we're meaning here}, that can 
be elaborated and modified accordingly, until it gets decapsulated and sent to 
$R$ eventually. When $R$ receives the packet, it is not be aware of the packet 
elaboration, since all the original headers were preserved (or slightly 
modified). TCP session recreation, instead, ``split'' the TCP session in two 
endpoints: an Ingress, that manage the connection with the client and an 
Egress, that communicate with the packet receiver. In order to achieve that, a 
session table needs to be established and continuously updated, while TCP 
headers need to be accordingly modified to allow data transmission through the 
Ingress and Egress points. TCP session recreation seems burdersome at the first 
sight, but it offers the flexibility to perform extensive packet manipulation: 
since the packet its recreated every time at the Ingress and Egress points, 
while in the Network Function Virtualization Infrastructure (NFVI), the 
original packet can be stripped of its headers (that could be saved in the 
session table) to slightly improve internal packet transmission. \todo{Insert 
TCP session recreation schema}

@@

In TCP Splitting, instead, we split the path from sender and receiver dividing
the end-to-end TCP connection into a multi-overlay-hop path where to each hop
we have an independant TCP cconnection. Each segment that composes the whole
path can use different flavours of TCP, e.g. using different enhancement based
on the tipology of the connection (in case of satellite connection we TCP Hybla
can be used, HighSpeed TCP in case of optical fiber). That could cause
performance issues depending on the intermediate proxies that create the route:
it is the case, for example, when an intermediate node sends back a spoofed ACK
before the original packet is delivered to the real consegnee. In that senario,
the sender unaware of the proxy, will miscalculate the sending window based on
the too low RTT. Other problems of TCP splitting are reliability andd security:
breacking the end to end TCP logic: a server failure is may cause to an unaware
client to believe that all packets reach the destination.

>>>>

TUN/TAP and IP over IP maintain the connection transparency incapsulating the
packet in another one. In this way, the original packet remains preserved and it
becomes the new packet payload\todo{Make an image showing a packet inside
  another packet, to make easy to understand what we're meaning here}, that can
be elaborated and modified accordingly, until it gets decapsulated and sent to
$R$ eventually. When $R$ receives the packet, it is not be aware of the packet
elaboration, since all the original headers were preserved (or slightly
modified). TCP session recreation, instead, ``split'' the TCP session in two
endpoints: an Ingress, that manage the connection with the client and an Egress,
that communicate with the packet receiver creating a multi-overlay-hop path
where for each hop there is an possible indipendent TCP connection. In order to
achieve that, a session table needs to be established and continuously updated,
while TCP headers need to be accordingly modified to allow data transmission
through the Ingress and Egress points. Nonetheless, care should be given to
packets path: in order to avoid ill-calculated congestion windows, the incoming
packets need to follow the same (or an equivalent one) path for the same
instatiated connection. This phenomenom is based on the intermediate proxies
that create the route: it is the case, for example, when an intermediate node
sends back a spoofed ACK before the original packet is delivered to the real
consegnee. In this senario, the sender, unaware of the proxy, will miscalculate
the sending window based on the too low RTT. Other problems of TCP splitting are
reliability and security, especially because the end to end TCP logic is no
longer maintained: a server failure may cause to an unaware client to believe
that all the packets have reached the destination. TCP session recreation seems
burdersome and it doesn't seem to add any significant benefit at the first
sight, but it offers the flexibility to perform extensive packet manipulation:
since the packet its recreated every time at the Ingress and Egress points,
while in the Network Function Virtualization Infrastructure (NFVI), the original
packet can be stripped of its headers (that could be saved in the session table)
to slightly improve internal packet transmission. \todo{Insert TCP session
  recreation schema} On top of that, it offers the possibility to use different
TCP flavours, hence increasing the communication speed in heterogeneous networks
(e.g. in case of satellite connections TCP Hybla can be employed, while it is
known that HighSpeed TCP gives best results when applied in optical fiber-based
connections).

@@
